Improving Day Ahead Electricity Load Forecasts with Google Trends

### 2014-07-29 Paper/DraftPaper.Rnw
graphics for statistically adjusted forecasts done.  BTW spotted an error in the hour two data.

  \subsection{PJM Load Forecasts and Actuals}
<<>>=
HourModelForecastCheck<-function(hour){
  Hour<-formatC(hour, width=2, flag="0")
  as.formula(paste("HE",Hour,"~ F",Hour,sep='' ))}

@@

>>>>

  \subsection{PJM Load Forecasts and Actuals}

<<>>=
HourModelForecastCheck<-function(hour){
  Hour<-formatC(hour, width=2, flag="0")
  as.formula(paste("HE",Hour,"~ F",Hour,sep='' ))}

@@

\begin{figure}
\begin{center}
\caption{Confidence Intervals for Intercept (95\%)}
<<echo=false,fig=TRUE>>=
library(ggplot2)
LowInter<-unlist(lapply(SAResults, FUN= function(x) confint(x) [1,1]))
HighInter<-unlist(lapply(SAResults, FUN= function(x) confint(x) [1,2]))
InterceptResults<-data.frame(1:24,LowInter,HighInter)
names(InterceptResults)[1]<-"Hour"

ggplot(InterceptResults, aes(Hour))+geom_pointrange(aes(y=LowInter, ymin=LowInter,ymax=HighInter))+geom_abline(intercept = 0)+ylab("Intercept Confidence Interval")
@
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\caption{Confidence Intervals for Co-Movement (95\%)}
<<echo=false,fig=TRUE>>=
library(ggplot2)
LowInter<-unlist(lapply(SAResults, FUN= function(x) confint(x) [2,1]))
HighInter<-unlist(lapply(SAResults, FUN= function(x) confint(x) [2,2]))
InterceptResults<-data.frame(1:24,LowInter,HighInter)
names(InterceptResults)[1]<-"Hour"

ggplot(InterceptResults, aes(Hour))+geom_pointrange(aes(y=LowInter, ymin=LowInter,ymax=HighInter))+geom_abline(intercept = 1,slope=0)+ylab("Intercept Confidence Interval")
@
\end{center}
\end{figure}

<<>>=
library(ggplot2)
ggplot(WTrends)+
geom_point(aes(F01,HE01,shape='a'))+geom_point(aes(F02,HE02,shape="b"))+
geom_point(aes(F03,HE03,shape='c'))+geom_point(aes(F04,HE04,shape="d"))+
geom_point(aes(F05,HE05,shape='e'))+geom_point(aes(F06,HE06,shape="f"))+
geom_abline(intercept = 0, slope = 1)
@
